\ttitle

### 2014-01-16 Chapters/Chapter4/change_detection.tex
Algorithm Chapter 4

\begin{table}
\begin{center}
  \caption[Proposed algorithm]{Algorithm of the proposed change detection method, using the Ratio-Thresholding method of \ref{subsec:ratio_thresholding} for change detection.}
  \begin{tabular}{ l p{12cm} }
    \hline
    Step & Action \\
    \hline
    & \textbf{Input:} time series $\vectorsym{x}$, window size $n$ \\
    & \textbf{Output:} collection of change points $\vectorsym{t}$ \\
    1 & Start with $n$ data objects as working set and construct hypersphere \\
    2 & Add next data object $x_t$ and drop first one \\
    3 & Identify new hyper-sphere and its \emph{approximate radius} \\
    4 & Calculate radius average of hyperspheres since last change point \\
    5 & Calculate radius ratio $\hbar$. \newline
    If $\hbar$ is  lower than ${th}_{low}$ or greater than ${th}_{high}$ then mark $t$ as change point in $\vectorsym{t}$ \\
    6 & Continue from step 2, until no more data objects available \\
    7 & Apply post-processing: merge close change points \\
    \hline
  \end{tabular}
  \label{tab:algorithm_proposed_method}
\end{center}
\end{table}

\TODO{Algoritme meer in pseudo-code zetten. Prominenter maken.}

In the \gls{svcpd} the first step for a new data point $\vectorsym{z}$ is to check whether the data point lies within the enclosing (hyperspherical) boundary of the constructed model.
This will label the new data point as an in- or outlier, relative to the current data set.
Depending on that outcome, the model is updated to include the new data point.
The second step is to inspect the (changed) model properties, \ie the radius $R$.
In our method we only employ the second step: the inspection of the radius $R$.
We regard the first step (determine if $\vectorsym{z}$ is an outlier) to be superfluent: in case it is an outlier, the model update step will change the radius $R$ in order to let the boundary include the new data point $\vectorsym{z}$.
Would the new data object $\vectorsym{z}$ be already an inlier, then the updated model would not have a significant change in radius $R$.
Our algorithm is outlined in \Cref{tab:algorithm_proposed_method}.

>>>>

In the \gls{svcpd} the first step for a new data point $\vectorsym{z}$ is to check whether the data point lies within the enclosing (hyperspherical) boundary of the constructed model.
This will label the new data point as an in- or outlier, relative to the current data set.
Depending on that outcome, the model is updated to include the new data point.
The second step is to inspect the (changed) model properties, \ie the radius $R$.
In \gls{ocs-hats} we only employ the second step: the inspection of the radius $R$.
We regard the first step (determine if $\vectorsym{z}$ is an outlier) to be superfluent: in case it is an outlier, the model update step will change the radius $R$ in order to let the boundary include the new data point $\vectorsym{z}$.
Would the new data object $\vectorsym{z}$ be already an inlier, then the updated model would not have a significant change in radius $R$.
Our algorithm is outlined in \Cref{alg:ocs-hats}.

\begin{algorithm}
\caption{\acrlong{ocs-hats} algorithm.}
\label{alg:ocs-hats}
\begin{algorithmic}[1]
\Require time series $X$, window size $n$, thresholds $th_{low}$ and $th_{high}$, proximity factor $p$
\Ensure collection $change\_points$
\item[]
\State $change\_points \leftarrow$ empty collection
\State $radii \leftarrow$ empty collection
\State Initialize $w \leftarrow incremental\_svdd$ with first $n$ samples from $\vectorsym{x}$
\item[]
\While{ new sample $x$ from $X$ at time $t$}
  \item[]
  \State Add $x$ to $w$
  \State $sphere \leftarrow update\_hypersphere(w)$
  \State $radius \leftarrow extract\_radius(sphere)$
  \State $radii[t] \leftarrow radius$
  \item[]
  \State $\hbar \leftarrow$ calculate ratio from previous average $radii$ and current $radius$
  \item[]
  \If{ $\hbar$ \textless \, $th_{low}$ \textbf{or} $\hbar$ \textgreater \, $th_{high}$} %\Comment{Compare $\hbar$ with thresholds}
    \State Add current time $t$ to $change\_points$
    \State Empty previous $radii$
  \EndIf
  \item[]
  \State Remove oldest $x$ from $w$
\EndWhile

\item[]

\State Merge $\vectorsym{cp}$ based on proximity $p$
\end{algorithmic}
\end{algorithm}
